### 2019-06-18 initial/notes.tex
check in WIP

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$.

>>>>

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$. Let's consider a model where $\dot{\eta} = +\epsilon \eta \mu$.
It should be noted that, upon careful calculation, $\dot{\eta} = -\epsilon \eta
\mu$ will \emph{not} result in any captures! Our choice only permits captures
\emph{from top down}. We will see this below.

Our expression then becomes:
\begin{align*}
    B_i &= \int -\frac{\epsilon \mu}{2\alpha^2}\s*{
        \alpha^2 \mu^2 - \cos^2 I}\;\mathrm{d}t,\\
        &\approx -\frac{\epsilon}{2\alpha^2} \int
            \mu \frac{\alpha^2 \mu^2 - \cos^2 I}{
                -\alpha \mu + \cos I}\;\mathrm{d}\phi,\\
        &\approx +\frac{\epsilon}{2\alpha^2}\int
            \mu\p*{\alpha \mu + \cos I}\;\mathrm{d}\phi.
\end{align*}
Now, we can evaluate our two integrals. The first integral is just over the top
leg, which is roughly
\begin{align*}
    \frac{B_{top}(2\alpha^2)}{\epsilon} &\approx
            \int\limits_{2\pi}^{0}\alpha \mu^2\;\mathrm{d}\phi,\\
        &\approx -2\pi \alpha \eta \sin I.
\end{align*}
The second integral around the full curve has two antisymmetric components, and
so (borrowing the old $\mu = \bar{\mu} + \mu'$ notation, where $\bar{\mu} =
\mu_4$ and $\mu'$ is antisymmetric over the two legs)
\begin{align*}
    \frac{B_{tot}(2\alpha^2)}{\epsilon} &\approx
        2\int\limits_{2\pi}^0 \alpha \bar{\mu}\mu'
            + \mu'\cos I\;\mathrm{d}\phi,\\
        &= -2\cos I A_{sep},\\
        &= -32\sqrt{\eta \sin I}\cos I.
\end{align*}
This predicts capture probability $P_c = \frac{16\cos I}{\pi \sqrt{\sin
I}}\sqrt{\eta}$. This doesn't seem to agree with our numerical integrations,
which suggest $P_c \propto \eta^1 I^0$, no dependence on $I$! There's a bit of
interpretation still, but that is WIP\@.

We can repeat this calculation using $\eta$ instead of $\alpha$ if desired, but
it doesn't give us any qualitatively different result.
